Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-25 mu/article/article.tex
Starting up V^{ab} description

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
    structure. The maximum response zone is localized for an energy range from
    0.90\,eV to 0.93\,eV. 145$^{\circ}$ and for a polarization angle of the
    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-vab-mag}
\end{figure}

@@

@@

$\varphi=153.8^{\circ}$ and the spin angle over the $xy$ plane have is $\theta=290.4^{\circ}$.

@@

\subsection{Fixing spin} % (fold)
\label{sec:res-fixspin}

% subsection res-fixspin (end)

>>>>

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
    structure. The maximum response zone is localized for an energy range from
    0.90\,eV to 0.93\,eV and for a polarization angle of the
    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-vab-mag}
\end{figure}

@@

% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %%        alt-plots/alt-3d-vab.gp

@@

$\varphi=153.8^{\circ}$ and the spin angle over the $xy$ plane have is
$\theta=290.4^{\circ}$.

@@

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-vab-mag-1}
\end{figure}
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The local maximum response zone is localized for an energy range
    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
    from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-vab-mag-2}
\end{figure}

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-1}
\end{figure}
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
    \caption{Intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-2}
\end{figure}
